Capstone Movielens Report

### 2025-02-01 reports/capstone-movielens-report.Rmd
Devepment in progress.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex

  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

```{r setup, include=TRUE, echo = FALSE}
library(RefManageR)
bib <- ReadBib("references.bib", check = FALSE)
BibOptions(check.entries = FALSE,
           hyperlink = "to.bib",
           bib.style = "numeric", 
           style = "markdown", 
           cite.style = 'numeric')

citeB <- function(citeKey){
  Cite(bib, citeKey, .opts = list(super = FALSE))
}

@@

PrintBibliography(bib,
                  .opts = list(check.entries = FALSE,
                               hyperlink = "to.bib",
                               first.inits = FALSE,
                               bib.style = "numeric",
                               style = "markdown",
                               cite.style = 'numeric'))

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex
  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
    - \hypersetup{backref,
          pdfpagemode=FullScreen,
          colorlinks=true,
          implicit=false}
    #- \hyper@nopatch@bib = null
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

```{r setup, include=TRUE, echo = FALSE}
library(RefManageR)
bib <- ReadBib("references.bib", check = FALSE)

BibOptions(check.entries = FALSE,
           hyperlink = "to.bib",
           bib.style = "numeric", 
           style = "markdown", 
           cite.style = 'numeric')

bibFound <- SearchBib(bib)

citeB <- function(citeKey){
  Cite(bibFound[citeKey], .opts = list(super = FALSE))
}

@@

PrintBibliography(bibFound,
                  .opts = list(check.entries = FALSE,
                               hyperlink = "to.bib",
                               first.inits = FALSE,
                               bib.style = "numeric",
                               style = "markdown",
                               cite.style = 'numeric'))
